\thesistitle

### 2019-07-25 sections/research.tex
New table stuff

\begin{table}[H]
 \begin{center}
  \caption{Our survey on clone detection tools.} \label{table:dettools}
  \medskip
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
Siamese \cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
NiCAD \cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
CPD \cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
CCFinderSW \cite{semura2017ccfindersw}   &    &             &             & \checkmark            \\ \hline
\begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
BigCloneEval \cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
Deckard \cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
\end{tabular}
\end{center}
\end{table}

>>>>

\begin{table}[H]
 \begin{center}
  \caption{Our survey on clone detection tools.} \label{table:dettools}
  \medskip
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
Siamese~\cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
NiCAD~\cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
CPD~\cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
\begin{tabular}[c]{@{}l@{}}CCFinder~\cite{kamiya2002ccfinder}\\ D-CCFinder~\cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
CCFinderSW~\cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
\begin{tabular}[c]{@{}l@{}}SourcererCC~\cite{sajnani2016sourcerercc}\\ Oreo~\cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
BigCloneEval~\cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
Deckard~\cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
Scorpio~\cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
\end{tabular}
\end{center}
\end{table}
